Exploring how changes in age at death and cause of death have narrowed the black-white life expectancy gap over forty-five years in the United States.

### 2017-02-09 Manuscript/Manuscript_COD_decomp.Rmd
age factor levels

age_decomp_results$age <- factor(age_decomp_results$age, levels = levels(age_decomp_results$age)[c(1, 2, 11, 3:10, 12:19)])

>>>>

age_decomp_results$age <- factor(age_decomp_results$age, levels = levels(age_decomp_results$age)[c(1, 2, 11, 3:10, 12:19)])
age_cod_results$age <- factor(age_cod_results$age, levels = levels(age_cod_results$age)[c(1, 2, 11, 3:10, 12:19)])                                                             
```
